Region-Network Hierarchical Sparsity Priors for\\ High-Dimensional Inference in Brain Imaging

### 2016-02-05 paper/icml2016/example_paper.tex
scikit-learn
typo

% \paragraph{Implementation.}
\subsection{Implementation}
All analyses were performed in Python.
We used \textit{nilearn} to process and resphape
the extensive neuroimaging data 
\cite{abrah14},
\textit{scikit learn} to design machine-learning
data processing pipelines
\cite{pedr11},
and
\textit{SPAMs} for numerically optimized
implementations of the sparse estimators
(\url{http://spams-devel.gforge.inria.fr/}).
All Python scripts that generated the results are
accessible online for reproducibility and reuse
(\url{http://github.com/anonymous/anonymous}).
% (\url{http://github.com/banilo/nips2015}).

%
\subsection{Data}
% \paragraph{Data.}
As the currently biggest openly-accessible reference dataset,
we chose resources from the Human Connectome Project (HCP)
\cite{barch2013}.
Neuroimaging task data with labels of ongoing cognitive processes
were drawn from 500
healthy HCP participants (cf. Appendix for details on datasets).
18 HCP tasks 
were selected that are known to elicit reliable neural activity
across participants.
% across participants (Table \ref{table_tasks}).
In sum, the HCP task data incorporated 8650 first-level activity maps
from 18 diverse paradigms administered to 498 participants (2 removed
due to incomplete data).
All maps were resampled to a common $60\times72\times60$ space of
3mm isotropic voxels and gray-matter masked (at least 10\% tissue
probability).
The supervised analyses were thus based on labeled HCP task maps with
79,941 voxels of interest representing z-values in gray matter.

>>>>

% \paragraph{Implementation.}
\subsection{Implementation}
All analyses were performed in Python.
We used \textit{nilearn} to process and resphape
the extensive neuroimaging data 
\cite{abrah14},
\textit{scikit-learn} to design machine-learning
data processing pipelines
\cite{pedr11},
and
\textit{SPAMs} for numerically optimized
implementations of the sparse estimators
(\url{http://spams-devel.gforge.inria.fr/}).
All Python scripts that generated the results are
accessible online for reproducibility and reuse
(\url{http://github.com/anonymous/anonymous}).
% (\url{http://github.com/banilo/nips2015}).

%
\subsection{Data}
% \paragraph{Data.}
As the currently biggest openly accessible reference dataset,
we chose resources from the Human Connectome Project (HCP)
\cite{barch2013}.
Neuroimaging task data with labels of ongoing cognitive processes
were drawn from 500
healthy HCP participants (cf. Appendix for details on datasets).
18 HCP tasks 
were selected that are known to elicit reliable neural activity
across participants.
% across participants (Table \ref{table_tasks}).
In sum, the HCP task data incorporated 8650 first-level activity maps
from 18 diverse paradigms administered to 498 participants (2 removed
due to incomplete data).
All maps were resampled to a common $60\times72\times60$ space of
3mm isotropic voxels and gray-matter masked (at least 10\% tissue
probability).
The supervised analyses were thus based on labeled HCP task maps with
79,941 voxels of interest representing z-values in gray matter.
